Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-25 draft.tex
caption changes

					\caption{The general architecture format for the models used in these
					experiments. In every feature, as well as in the terminus, there can be
					various kinds of hidden layers.}

@@

					\includegraphics[width=0.4\textwidth]{images/submodel.png}

@@

					with the output as a flattened vector.}

@@

					\includegraphics[width=0.4\textwidth]{images/term_model.png}
					\caption{A generalized representation of a terminus model, which can have a
					varying amount of hidden layers.}

>>>>

					\caption{The general architecture for the models used in these experiments,
					containing \(n\) features. The features are processed in their tailored
					sub-models before being processed together in the terminus model.}

@@

					\includegraphics[width=0.7\textwidth]{images/submodel.png}

@@

					with the output as a flattened vector. Here, \(n\) is the number of
					convolutional-pooling pairs.}

@@

					\includegraphics[width=0.7\textwidth]{images/term_model.png}
					\caption{A generalized representation of the terminus model paired with \(n\)
					sub-models and containing \(m\) hidden layers.}
